\LARGE \bf Human-Robot Interaction: A Deliberative Architecture

### 2013-07-25 paper.tex
Added section on Embodied Cognition

@@

>>>>

\fxwarning{robot control architecture for service robots: what else?}

@@

\subsection{Embodied Cognition}

Robotics is traditionally regarded as the prototypical testbed for \emph{embodied}
artificial intelligence, and this dimension is especially prevalent in
human-robot interaction, where agents have to share a joint physical
environment.

It results in a tight coupling between the symbolic and the geometric realms:
while AI at its origins was mostly a matter of symbolic models, it has been
since recognised that not only the mind is not a purely abstract system,
disconnected from the physical world, but even more, cognition fundamentally
relies on its relation to the physical world (so-called \emph{embodied
cognition}). Varela~\cite{Varela1992} is one of the main discoverer of these
mechanisms, and coined the concept of \emph{enactivism} as the theoretical
framework that study the links between cognition, embodiment and actions.

The challenge of symbol grounding is tightly linked to this issue. It
corresponds to the identification or creation, and then, maintenance of a link
between the symbol (the syntactic form of knowledge the computer will
manipulate) and its semantics, \ie its meaning, anchored in the world (the
relations between the symbol, the referent of the symbol, and mediating minds
is classically referred as the \emph{semantic triangle}, and has been
extensively studied in linguistics). The issue of grounding is well known in
cognitive science and is summarised by Harnard~\cite{Harnad1990} by this
question: ``how the semantic interpretation of a formal symbol system can be
made intrinsic to the system?''. This issue has a major practical importance in
robotic: for a robot to be both endowed with a symbolic representational and
reasoning system, and able to \emph{act} in the physical world, it must ground
its knowledge.

Grounding is implemented at different levels in our architecture. The main source
of grounded symbolic knowledge is the situation assessment module, {\sc Spark}.
Not only it builds symbolic facts from spatial reasoning, but it also relies on
temporal reasoning to track the world state and build explanations to interpret
unexpected perceptions (we mentioned above the example of a disappearing
object).

Because {\sc Spark} is also able to track humans, which enables in turn
perspective-aware spatial reasoning, it produces grounded symbolic knowledge
for interacting agents as well. This is a typical \emph{embodied} cognitive
skill.

Grounding also occurs during verbal and non-verbal communication. The {\sc
Dialogs} module grounds new concepts introduced by the speaker by asking questions
until it can attach the new concept to concepts already present in the
knowledge pool (typically, if I ask the robot ``bring me a platypus'', the
robot asks ``what is a platypus''. I may answer ``a mammal'' and the robot will
ask ``what is a mammal?'' and so on until it anchors the new concepts to ones
it already knows). Non verbal interaction (like gestures) is also partially
grounded. When the user points at something, it can say ``give me this'' and
the robot grounds \emph{this} to the pointed artifact.

Because only objects marked with tags are currently recognized (in our typical
lab experiments, it may be a dozen of them), the robot grounding mechanisms work
in a small-sized closed world. This assumption obviously greatly facilitates
the task. It remains to be seen if systematic marking of manipulated objects
(for instance with RFID tags) is a realistic path. It may be the case if the
robot is expected to be used in a well-defined, slowly changing environment.
Real-time recognition of large libraries of objects is another path which may
be viable soon~\cite{Dean2013Fast}.
